---
title: "Inverse Wishart Bias"
output: html_document
---

Covariance matrix estimation  

* Multivariate normal sampling models 
* random-intercept, random-slope models 

$ 
y_{ij} = \beta_{0j} + \beta_{1j} x_{ij} + \beta_{2j}z_{ij} + \epsilon_{ij} 
$


\begin{pmatrix} \beta_{0j} \\ \beta_{1j} \\ \beta_{2j} \end{pmatrix} &\sim&  N \left( \begin{pmatrix} \mu_{0} \\ \mu_{1} \\ \mu_{2} \end{pmatrix} , \Sigma \right) , \;\;\; \epsilon_{ij} \sim N(0, \sigma^2) 



```{r, pkgs }
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
```



```{r}
# PART I: Simulations results, plots and tables
res  <- read.table('data/reduced_res.csv', header=T)

# reorder and relabel prior factor
res$prior.old <- res$prior
res$prior <- factor(res$prior, levels=c('iw','siw', 'ht', 'ss'),labels=c('IW','SIW', 'HIWht', 'BMMmu'))
#rescov$prior <- factor(rescov$.id, levels=c('iw','siw', 'ht', 'ss'),labels=c('IW','SIW', 'HIWht', 'BMMmu'))
# with(res, table(prior,prior.old))

# for compare against pearson instead to true value
load('data/simdata.Rdata')
corr <- ddply(simdata.2, .(s,sim,r,ns), summarize, pearson=cor(X1,X2))
res.p <- merge(res, corr)
```

You can also embed plots, for example:

```{r, echo=FALSE}
d <- subset(res.p, param=='rho')
d$rx <- d$r + runif(nrow(d),-.05,.05)
d$ns <- factor(d$ns, levels=c(10,50,250), labels=paste('n',c(10,50,250),sep='=='))
d$s <- factor(d$s, levels=c(0.01,0.1,1,10,100), labels=paste('sigma',c(0.01,0.1,1,10,100),sep='=='))
qplot(data=d ,x=pearson, y=mean,color=prior,shape=prior,xlab='True Correlation', ylab='Posterior Mean') + 
  facet_grid(facets=ns~s,scales='free',labeller=label_parsed) + geom_abline(1) + theme(legend.position= 'bottom') + scale_x_continuous(breaks=c(0,0.5,1))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
